### 2011-09-21 doc/theses/vitasek/chapter-4-1-experiments-setup.tex
Thesis: in progress.

A short reasoning for this choice: realistic - we want to see the performance in cases taken from the real world. The problem with realistic data is that sometimes, interesting values (that might or might not contain IDs) are stored as simple text nodes instead of attributes. We will try to convert some of these values to attributes (e.g. using a smart XSL transformation), let our heuristics find the ID sets, and then translate them back to XML keys (see \ref{realistic-converted} for details).
And finally, we create completely artificial data to create inputs that will put our heuristics in stress. This is because the realistic data often prove to be too easy to solve - the list of candidate AMs is usually too short to be hard to be solved to optimality.\\

To understand these data sets we will discuss their origin and \textit{graph representation}. As mentioned earlier, % TODO link
the problem of finding the optimal ID set is in fact the problem of finding the maximum weighted independent set in a graph. Therefore it is interesting to actually see the graphs of these data sets and understand some related metrics.

The former will be achieved with the help of GraphViz tool, % TODO link
where we will draw the graphs so that all the vertices represent the \textit{candidate AMs}, and the edges represent pairs of AMs that have nonempty intersection of their images (and thus cannot be in the same ID set together). Thus solving the maximal weighted IS on these graphs will be equivalent to solving our problem of optimal ID set.

@@

% TODO their DTD/XSD - do we have ID attributes?

@@

Our aim is to create a graph with around $v$ vertices and $e$ edges. First, we introduce $v$ elements with names \texttt{vertex0} - \texttt{vertex\{V-1\}}. To constitute an AM, they need an attribute \texttt{attr}, but with large enough random values, so that these values will not conflict with any others. Second, for each of the $e$ edges we choose two \texttt{vertex*} elements at random, and give them the same value of their \texttt{attr}. This will ensure they cannot share the same ID set, thus effectively creating the edge in the graph representation.

@@

While studying the tables it becomes obvious that the actual numbers $|V|$ and $|E|$ do not match to the $v$ and $e$ in the names of the sets. This is because how the random generation algorithm works: it might pick the same edge twice, which will automatically render it unsuitable for the ID set. Because of the so-called Birthday paradox, % TODO link
this will happen more with higher $e$.

>>>>

A short reasoning for this choice: realistic - we want to see the performance in cases taken from the real world. The problem with realistic data is that sometimes, interesting values (that might or might not contain IDs) are stored as simple text nodes instead of attributes. We will try to convert some of these values to attributes (e.g. using a smart XSL transformation), let our heuristics find the ID sets, and then translate them back to XML keys (see \ref{realistic-converted} for details).
And finally, we create completely artificial data to create inputs that will put our heuristics in stress. This is because the realistic data often prove to be too easy to solve - the list of candidate AMs is usually too short to be hard to be solved to optimality.

\begin{define}[Data set]
	\label{define-data-set}
	One or more XML files sharing the same schema (even if only an implicit schema) shall be referred to as a \textit{data set}. In the scope of this work this will always mean a \textit{single} XML file. However, this definition of a data \textit{set} covers also the extension to more XML files as described in \cite{fidax}.
\end{define}

To understand our test data sets we will discuss their origin and \textit{graph representation}. As mentioned earlier, % TODO link
the problem of finding the optimal ID set is in fact the problem of finding the maximum weighted independent set in a graph. Therefore it is interesting to actually see the graphs of these data sets and understand some related metrics.

The former will be achieved with the help of GraphViz tool (\cite{graphviz}), where we will draw the graphs so that all the vertices represent the \textit{candidate AMs}, and the edges represent pairs of AMs that have nonempty intersection of their images (and thus cannot be in the same ID set together). Thus solving the maximal weighted IS on these graphs will be equivalent to solving our problem of optimal ID set.

@@

@@

Our aim is to create a graph with approximately $v$ vertices and $e$ edges. First, we introduce $v$ elements with names \texttt{vertex0} - \texttt{vertex\{V-1\}}. To constitute an AM, they need an attribute \texttt{attr}, but with large enough random values, so that these values will not conflict with any others. Second, for each of the $e$ edges we choose two \texttt{vertex*} elements at random, and give them the same value of their \texttt{attr}. This will ensure they cannot share the same ID set, thus effectively creating the edge in the graph representation.

@@

While studying the tables it becomes obvious that the actual numbers $|V|$ and $|E|$ do not match to the $v$ and $e$ in the names of the sets. This is because how the random generation algorithm works: it might pick the same edge twice, which will automatically render it unsuitable for the ID set. Because of the so-called Birthday paradox (see e.g. \cite{birthday}), this will happen more with higher $e$.
